---
title: "Crediblemeds_ATC_DDIs"
author: "Jorge H."
date: "2/3/2020"
knit: (function(inputFile, encoding) { 
      out_dir <- 'html_files';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, 'Crediblemeds_DDI.html')) })

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
```

Packages used
```{r}
library(readxl)
library(readr)
library(data.table)
library(plyr)
library(tidyr)
```

# Tyding and merging to ATC

Looking at DDI file
```{r}
CredibleMeds_DDIs <- read_excel("Lists/CredibleMeds_DDIs.xlsx")

# Fixing 'Related drug' option
CredibleMeds_DDIs[9,"Related Drugs"] <- CredibleMeds_DDIs[9,"Options"]
CredibleMeds_DDIs[9,"Options"] <- CredibleMeds_DDIs[9,"...9"]

CredibleMeds_DDIs[10,"Related Drugs"] <- CredibleMeds_DDIs[10,"Options"]
CredibleMeds_DDIs[10,"Options"] <- CredibleMeds_DDIs[10,"...9"]

# Proceed to eliminate the ...9 column. 
CredibleMeds_DDIs["...9"] <- NULL 

```


From Drugbank to ATC
```{r}
drug_atc_codes <- read_csv("Lists/drug_atc_codes.csv")

# Merging
DDI_mapped <- merge(CredibleMeds_DDIs,drug_atc_codes[,c(1,10)],
                    by.x="object_drugbank",
                    by.y = "parent_key")

DDI_mapped <- merge(DDI_mapped,drug_atc_codes[,c(1,10)],
                    by.x="precipitant_drugbank",
                    by.y = "parent_key")
```


Additionals
```{r}
# Adding proper names
setnames(DDI_mapped,
         old = c("atc_code.y","atc_code.x"),
         new = c("drug", "codrug"))

# Adding columns of first level of ATC
DDI_mapped$level_1_atc_drug <- substr(DDI_mapped$drug,1,1)
DDI_mapped$level_1_atc_codrug <- substr(DDI_mapped$codrug,1,1)

# Unifying ATC columns so to have them as vectors also.
DDI_mapped$ATC_vector <- paste(DDI_mapped$drug,DDI_mapped$codrug, sep = "_") 
```


# FACTORISING

Factorising *Mechanism of action* feature 
```{r}
# Factorising Mechanism of actions
DDI_mapped$Mechanism_of_action <- ''
row <- 1

for (cell in DDI_mapped[,"Mechanism"]){
  
  if (grepl("Inhibition", cell) & 
     (grepl("metabolism", cell) | grepl("metabolite", cell)) & 
      grepl("CYP", cell)){
    
        DDI_mapped[row,"Mechanism_of_action"] <- sapply(
          DDI_mapped[row,"Mechanism_of_action"], 
          function(x) 
            paste("CYP_inhibition",x)
        )
  }
  
  if (grepl("Inhibition", cell) &
      grepl("transport", cell)){
    
        DDI_mapped[row,"Mechanism_of_action"] <- sapply(
          DDI_mapped[row,"Mechanism_of_action"],
          function(x) 
            paste("Transport_inhibition",x)
        )
  }
  
  if (grepl("Antiplatelet effects", cell) & 
      grepl("GI erosion", cell)){
    
        DDI_mapped[row,"Mechanism_of_action"] <- sapply(
          DDI_mapped[row,"Mechanism_of_action"], 
          function(x) 
            paste("Antiplatelet_effects_and_GI_erosion",x)
        )
  }
  if (grepl("depletion", cell) & 
      grepl("vitamin K", cell)){
    
        DDI_mapped[row,"Mechanism_of_action"] <- sapply(
          DDI_mapped[row,"Mechanism_of_action"], 
          function(x) 
            paste("Depletion_of_vitamin_K",x)
        )
  }
  
  row <- row + 1
} 
```


Factorising *Management* feature
```{r}
# Factorising Management
DDI_mapped$Management <- ''
row <- 1

for (cell in DDI_mapped[,"Options"]) {
  
  if (grepl("Usually Avoid", cell)){
    
    DDI_mapped[row,"Management"] <- sapply(
      DDI_mapped[row, "Management"], 
      function(x) 
        paste("Usually_avoid",x)
    )
  }
  
  if (grepl("Take Precautions", cell)){
    
    DDI_mapped[row,"Management"] <- sapply(
      DDI_mapped[row, "Management"], 
      function(x) 
        paste("Take_precautions",x)
    )
  }
  row <- row + 1
}

remove(row)
remove(cell)

# Saving tables with preferred sortening
DDI_mapped <- DDI_mapped[,c(10,9,1,2,4,3,5,6,7,8,14,15,11:13)]
```


# Saving different types of documents for posterior analysis. 

Filtering Crediblemeds DDIs that can be observed in the clinical data 
```{r}
clinicaldrugpairs_counts <- read_delim("Lists/clinicaldrugpairs_counts.tsv",
                                       "\t", 
                                       escape_double = FALSE, 
                                       trim_ws = TRUE
                                       )


DDI_mapped_subset <- merge(DDI_mapped,
                           clinicaldrugpairs_counts[,1:2],
                           by = c("drug", "codrug")
                           )
```


Saving table with all information for compendia and clinical data
```{r}
# Compendia
write.table(DDI_mapped,
            "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/ATC_treatment/Filtered_datasets/Crediblemeds_to_ATC.txt",
            sep = "\t",
            row.names = FALSE 
            )

# Clinical data
write_csv(DDI_mapped_subset,
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/ATC_treatment/DDI_clinical_data/DDI_dataset/Crediblemeds_DDI.txt"
          )
```


Saving ATC vector for clinical data
```{r}
# Clinical data
filese <- file("C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/ATC_treatment/DDI_clinical_data/DDI_atc_vector/Crediblemeds_vector.txt")
writeLines(c(DDI_mapped_subset$ATC_vector), filese)
close(filese)
```


Saving datasets with their respective *feature* column for clinical data
```{r}
# Saving all DDIs with the feature mechanism of action
write_csv(DDI_mapped_subset[DDI_mapped_subset$Mechanism_of_action != '',c(1,2,11,13,14)],
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/Features/Mechanism_of_action/Crediblemeds_M.A_DDI.txt",
          col_names = FALSE
          )


# Saving all DDIs with the feature management
write_csv(DDI_mapped_subset[DDI_mapped_subset$Management != '',c(1,2,12,13,14)],
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/Features/Management/Crediblemeds_management_DDI.txt", 
          col_names = FALSE
          )
```

