---
title: "Exploring_KEGG_dataset"
author: "Jorge H."
date: "17/2/2020"
knit: (function(inputFile, encoding) { 
      out_dir <- 'html_files';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), out_dir, '2_KEGG_dataset (1).html')) })
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)
```

```{r}
library(readr)
```

```{r}
KEEG_DDI <- read_csv("DDIs/KEEG_DDI.txt")
```

If using this document before running *Code_to_obtain_DDIs.R*, just run the part of ATC. The two following chuncks of code are designed to add a fifth column when downloading the raw data. 

The file *KEGG_DDI* is already processed and only needs mapping with ATCs. In future updates this files will be separated.



#Proceed to diferentiation of the mechanism of action
```{r}
#Used to pick the different targets (and plot number, plot to be inserted. It is the one of the first power point)
KEEG_DDI_target <- KEEG_DDI[grep("Target", KEEG_DDI$V4),]
KEEG_DDI_enzymes <- KEEG_DDI[grep("Enzyme", KEEG_DDI$V4),]
KEEG_DDI_CYP_inhibition <- KEEG_DDI[grep("CYP inhibition", KEEG_DDI$V4),]
KEEG_DDI_CYP_induction <- KEEG_DDI[grep("CYP induction", KEEG_DDI$V4),]
KEEG_DDI_transporter_inhibition <- KEEG_DDI[grep("Transporter inhibition", KEEG_DDI$V4),]
KEEG_DDI_transporter_induction <- KEEG_DDI[grep("Transporter induction", KEEG_DDI$V4),]
KEEG_DDI_same_components <- KEEG_DDI[grep("same components", KEEG_DDI$V4),]
KEEG_DDI_enzyme_target <- KEEG_DDI[grep("Enzyme-Target", KEEG_DDI$V4),]
```


#Creating new column for mechanism of action
```{r}
#Extra column to give a better characterization of the different targets each DDIs is involved in.
vector_number_of_targets <-c()
KEEG_DDI$V5 <- ""
j <- 1
for (i in KEEG_DDI[,4]){
  
  if (grepl("same components",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Same components",x))
  }
  
  if (grepl("(^|[^-])Target",i, perl = TRUE)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Target(Gene)",x))
  }
  
  if (grepl("Enzyme:",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Enzyme",x))
  }
  
  if (grepl("CYP inhibition",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("CYP_inhibition",x))
  }
  
  if (grepl("CYP induction",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("CYP_induction",x))
  }
  
  if (grepl("Transporter inhibition",i,fixed = TRUE)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Transporter_inhibition",x))
  }
  
  if (grepl("Transporter induction",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Transporter_induction",x))
  }
  
  if (grepl("Enzyme-Target",i)){
    KEEG_DDI[j,5] <- sapply(KEEG_DDI[j,5],function(x) paste("Target(Enzyme)",x))
  }
  
  j <- j + 1
  #print(j)
} 
KEEG_DDI$V5 <- sub("^$", "Unknown",KEEG_DDI$V5) #The ones that do not match any targets.
```

# Selecting the elements of management options ("CI","P","CI,P")
```{r}
KEEG_DDI <- KEEG_DDI[KEEG_DDI$V3 == "CI" | KEEG_DDI$V3 == "P" | KEEG_DDI$V3 == "CI,P",]
```

Wrtting file
```{r}
write_csv(KEEG_DDI, "DDIs/KEEG_DDI.txt")
```


Importing the clinical data
```{r}
clinicaldrugpairs_counts <-
  read_delim("Dataset_folder/clinicaldrugpairs_counts.tsv", 
  "\t", 
  escape_double = FALSE, 
  trim_ws = TRUE)
```

ATC
```{r}
KEEG_DDI <- read_csv("DDIs/KEEG_DDI")

kegg_to_atc <- read_table2("Mappings/kegg_to_atc.txt", 
    col_names = FALSE)

colnames(kegg_to_atc) <- c('kegg_identifier','atc_identifier')
kegg_to_atc$atc_identifier <- gsub('atc:','',kegg_to_atc$atc_identifier)


DDI_mapped <- merge(KEEG_DDI,kegg_to_atc,by.x = 'V1', by.y = 'kegg_identifier')
DDI_mapped <- merge(DDI_mapped,kegg_to_atc, by.x='V2',by.y = 'kegg_identifier')
DDI_mapped <- unique(DDI_mapped)


# Doing ATC duplicates

Table1 <- DDI_mapped[,c(7,6,2,1,3,4,5)]
Table2 <- DDI_mapped[,c(6,7,2,1,3,4,5)]
colnames(Table1) <- c("drug", "codrug", "drug1", "drug2", "Management", "M.A", "M.A (factorized)")
colnames(Table2) <- c("drug", "codrug", "drug1", "drug2", "Management", "M.A", "M.A (factorized)")

DDI_mapped <- rbind(Table1,Table2)

# Adding level 1 ATC
DDI_mapped$level_1_atc_drug <- substr(DDI_mapped$drug,1,1)
DDI_mapped$level_1_atc_codrug <- substr(DDI_mapped$codrug,1,1)

# Adding the pair of ATC joined
DDI_mapped$ATC_vector <-paste(
  DDI_mapped$drug,
  DDI_mapped$codrug, 
  sep = "_")

# Filtering to clinical data
DDI_mapped <- merge(
  DDI_mapped,
  clinicaldrugpairs_counts[,1:2],
  by = c("drug", "codrug")
  )
DDI_mapped <- unique(DDI_mapped)
```

Saving table with all information for compendia and clinical data
```{r}
# Clinical data
write_csv(DDI_mapped,
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/ATC_treatment/DDI_clinical_data/DDI_dataset/KEGG_DDI.txt"
          )
```

Saving ATC vector for clinical data
```{r}
# Clinical data
filese <- file("C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/ATC_treatment/DDI_clinical_data/DDI_atc_vector/KEGG_vector.txt")
writeLines(c(unique(DDI_mapped$ATC_vector)), filese)
close(filese)
```



Adding *management* feature.
```{r}
DDI_management <- DDI_mapped[,c(1,2,5,8,9)]

DDI_management <- unique(DDI_management)
DDI_management$Management <- gsub(',',' ',DDI_management$Management)

DDI_management <- DDI_management[!grepl("CI1",DDI_management$Management) & !grepl("P1",DDI_management$Management),]

write_csv(DDI_management,
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/Features/Management/KEGG_management_DDI.txt",col_names = FALSE)

```

Adding *mechanism of action* feature
```{r}
DDI_action <- DDI_mapped[,c(1,2,7,8,9)]

DDI_action <- unique(DDI_action)
DDI_action$`M.A (factorized)` <- gsub(',',' ',DDI_action$`M.A (factorized)`)
 
write_csv(DDI_management,
          "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/Features/Mechanism_of_action/KEGG_M.A_DDI.txt",col_names = FALSE)

```