---
title: "Twosides_features"
author: "Jorge H."
date: "14/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(dplyr)
```



Splitting files of TWOSIDES.csv (Do if necesity to update twosides database)
```{r}
TWOSIDES_to_split <- read_csv("Data/TWOSIDES.csv")


#CREATING MINI-DATASETS SO AS TO OPERATE EASILY
index <- sprintf("%d",1:10)
index_twosides_start <- 1
index_twosides_end <- 4292039   # Check that it matches
for (i in index){
  write_csv(TWOSIDES_to_split[index_twosides_start:index_twosides_end,],sprintf("Data/TWOSIDES_split/Twosides%s",i))
  index_twosides_start <- index_twosides_end
  index_twosides_end <- index_twosides_end + 4292039
}
Twosides10[4292041,] = TWOSIDES_to_split[42920391,]
  #Fixing last row missing
```



Merging the splitted_files
```{r}
Twosides_files <- list.files("Data/TWOSIDES_split/", full.names = T)
Twosides_files <- Twosides_files[grepl("*.txt", Twosides_files)]

TWOSIDES <- data.frame(drug_1_rxnorn_id = as.integer(),
                       drug_1_concept_name = as.character(),
                       drug_2_rxnorn_id = as.integer(),
                       drug_2_concept_name = as.character(),
                       A = as.integer(),
                       B = as.integer(),
                       C = as.integer(),
                       D = as.integer(),
                       PRR = as.numeric(),
                       PRR_error = as.numeric(),
                       mean_reporting_frequency = as.numeric(),
                       stringsAsFactors = FALSE)

for (i in Twosides_files){
  file = read_csv(i)
  file <- file[,c(1,3,5,11)] # It will work like that with a 8 GB RAM. Adding more may make R to crush.
  TWOSIDES <- rbind(TWOSIDES,file) #There may a error due to RAM requirements. Even with this subset files!
}
```

# TWOSIDES

We check
  + Number of different drugs.
  + Number of different diseases.
  + Number of different DDIs
  
```{r}
Unique_drugs1 <- unique(TWOSIDES$drug_1_rxnorn_id)
  # We have 1716 drugs

Unique_drugs2 <- unique(TWOSIDES$drug_2_rxnorm_id)
  # We have 1842 drugs

Total_unique_drugs <- c(Unique_drugs1,Unique_drugs2)
Total_unique_drugs <- unique(Total_unique_drugs)
  # We have 1917 drugs (Good_one)



Frequent_diseases <- as.data.frame(table(TWOSIDES$condition_concept_name))
Frequent_diseases <- Frequent_diseases[order(-Frequent_diseases$Freq),]
  # We observe 12726 diseases.
  # Checks most frequent diseases.



#Counting DDIs
Twosides_DDI <- TWOSIDES[,c("drug_1_rxnorn_id","drug_2_rxnorn_id")]

Twosides_DDI <- Twosides[!duplicated(Twosides_DDI[,c("drug_1_rxnorn_id","drug_2_rxnorn_id")]),]
```


A contingency table can be drawn using exposed and unexposed cohorts produced by propensity score matching.

                      Had outcome	  Didn't have outcome
Drug exposed	             A	             B
Not drug exposed	         C	             D

A	-> Number of reports prescribed the drug that had the condition

B	-> integer	Number of reports prescribed the drug that did not have the condition

C	-> integer	Number of reports not prescribed the drug† that had the condition

D	-> integer	Number of reports not prescribed the drug† that did not have the condition


## ATC mapping
+ From RXnorm to CUI
```{r}
RXNORM_to_CUI <- read_csv("Identifiers/RXNORM_to_cui")

colnames(RXNORM_to_cui)[1] <- "Class_id"
RXNORM_to_cui$`Class ID` <- gsub("http://purl.bioontology.org/ontology/RXNORM/","",RXNORM_to_cui$`Class ID`)

DDI_mapped <- merge(Twosides_DDI,RXNORM_to_CUI,by.x="X1",by.y = "Class_id")

DDI_mapped <- merge(DDI_mapped,RXNORM_to_CUI, by.x="X2",by.y = "Class_id")

DDI_mapped <- DDI_mapped[,c("CUI.x","CUI.y")]
#We loose 288 interactions
```


+ From CUI to ATC
```{r}
ATC <- read_csv("Identifiers/CUI_to_ATC.csv")

colnames(ATC)[1] <- "Class_Id"
ATC$Class_Id <- gsub("http://purl.bioontology.org/ontology/UATC/","",ATC$Class_Id)

DDI_mapped <- merge(DDI_mapped,ATC,by.x="CUI.x",by.y = "CUI")

DDI_mapped <- merge(DDI_mapped,ATC,by.x="CUI.y",by.y = "CUI")
```

+ Writting DDIs
```{r}
DDI_mapped <- DDI_mapped[,c("Class_Id.x","Class_Id.y")]

write.table(DDI_mapped,"C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/ATC_treatment/Filtered_datasets/Twosides_to_ATC.txt",sep = "\t",row.names = FALSE, col.names = FALSE)
```

## Transforming data

```{r}
#Selecting diseases that have a PRR value higher than 1
TWOSIDES <- TWOSIDES %>% filter(PRR > 1)

TWOSIDES_agreg_for <- aggregate(condition_meddra_id~drug_1_rxnorn_id+drug_2_rxnorm_id, data = TWOSIDES, paste, collapse = ',')


#From Rxnorm to CUI
TWOSIDES_agreg_for1 <- merge(TWOSIDES_agreg_for,RXNORM_to_cui[,c(1,6)], by.x="drug_1_rxnorn_id",by.y = "Class_id")

TWOSIDES_agreg_for1 <- merge(TWOSIDES_agreg_for1,RXNORM_to_cui[,c(1,6)], by.x="drug_2_rxnorm_id",by.y = "Class_id")

TWOSIDES_agreg_for <- TWOSIDES_agreg_for1[,c("CUI.x","CUI.y","condition_meddra_id")]

#From CUI to ATC
TWOSIDES_agreg_for2 <- merge(TWOSIDES_agreg_for,ATC[,c(1,6)],by.x="CUI.x",by.y = "CUI")

TWOSIDES_agreg_for2 <- merge(TWOSIDES_agreg_for2,ATC[,c(1,6)],by.x="CUI.y",by.y = "CUI")

TWOSIDES_agreg_for <- TWOSIDES_agreg_for2[,c(4,5,3)]

#Subsetting to the clinical data drugs
TWOSIDES_agreg_for <- TWOSIDES_agreg_for[TWOSIDES_agreg_for$Class_Id.x %in% subset_drugs_clinical_data$PRIM_ATC & TWOSIDES_agreg_for$Class_Id.y %in% subset_drugs_clinical_data$PRIM_ATC,]

write_csv(TWOSIDES_agreg_for, "C:/Users/Jorge_TEMP/Desktop/Thesis_Bibliography/DDI_datasets/Analysis/Features/Side_effects/DDI_twosides_side_effect.txt")
```






# OFFSIDES; side-effect of each drug
```{r}
UNICOS <- duplicated(OFFSIDES$drug_rxnorn_id)

# There are 2730 drugs with side-effects

# There are in total 3,206,558 side effects.
```